Source Code Volatility Metric

### 2020-04-19 paper/article.tex
more

\documentclass[sigconf]{acmart}
\title{Source Code Volatility Metric}
\author{Yegor Bugayenko}{}{}
\ccsdesc[100]{Software and its engineering~Metrics}
\keywords{Metrics, Software Size, Software Maintainability}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{verbatimbox}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{minted}
  \setminted{fontsize=\footnotesize}
  \setminted{breaklines}
  \usemintedstyle{bw}
\newcommand{\code}[1]{\texttt{#1}}
\newenvironment{nicetable}
  {\setlength{\parindent}{0em}\medskip\small}
  {\medskip}
\input{total}
\begin{document}
\begin{abstract}
A new metric was introduced to calculate the distance
between actively modified files in a source code repository
and the files, which are rarely modified and may be considered
as ``dead'' or ``abandoned.'' It was empirically demonstrated that larger repositories
have larger values of the introduced metric.
The metric may be used for earlier detection of code maintenance anomalies
and helping software developers make the decision of splitting the repository
into smaller oners in order to prevent maintainability issues.
\end{abstract}
\maketitle

@@

>>>>

\documentclass[sigconf]{acmart}
\title{Source Code Volatility Metric}
\author{Yegor Bugayenko}{}{}
\email{yegor.bugayenko@huawei.com}
\affiliation{%
  \institution{Huawei Technologies Co., Ltd.}
  \city{Moscow, Russia}
}
\ccsdesc[100]{Software and its engineering~Metrics}
\keywords{Metrics, Software Size, Software Maintainability}
\setcopyright{acmcopyright}
\copyrightyear{2020}
\acmYear{2020}

\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{verbatimbox}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{minted}
  \setminted{fontsize=\footnotesize}
  \setminted{breaklines}
  \usemintedstyle{bw}
\newcommand{\code}[1]{\texttt{#1}}
\newenvironment{nicetable}
  {\setlength{\parindent}{0em}\medskip\small}
  {\medskip}
\input{total}
\begin{document}
\begin{abstract}
A new metric was introduced to calculate the distance
between actively modified files in a source code repository
and the files, which are rarely modified and may be considered
as ``dead'' or ``abandoned.'' It was empirically demonstrated that larger repositories
have larger values of the introduced metric.
The metric may be used for earlier detection of code maintenance anomalies
and helping software developers make the decision of splitting the repository
into smaller ones in order to prevent maintainability issues.
\end{abstract}
\maketitle

@@

GitHub\texttrademark{} (currently owned by Microsoft\texttrademark{}) is
one of the largest platforms for \emph{open source} projects.
GitHub provides free access to all public Git repositories, which makes it possible
to analyze Git histories.
